Conflict-Free Vertex Coloring of Planar Graphs

### 2017-04-10 presentation/presentation.tex
Working on algorithm presentation

\usepackage{graphicx}
\usepackage[scale=2]{ccicons}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[absolute,overlay]{textpos}
% \usepackage[texcoord,grid,gridunit=mm,gridcolor=red!10,subgridcolor=green!10]
% {eso-pic}

@@

@@

    \begin{textblock*}{14cm}(1cm, 7.1cm) % {block width} (coords)
      To be conflict-free colored with 1 color, graph $G$ cannot contain $K_3$ or $K_4^{-3}$ as a minor. A graph is a \textbf{minor} if it can be formed by deleting and/or contracting edges from its parent graph.
    \end{textblock*}

@@

    \begin{algorithm}[H]
    \caption{Test}
    \scriptsize
    \begin{algorithmic}[1]
    \State $i \gets 1$
    \State Remove all isolated paths from $G$
    \While{$G$ is not empty}
    	\State $D \gets \emptyset$
    	\ForAll{components of $G$}
    		\State Pick any vertex $v$
    		\State $D \gets D \cup \{ v \}$
    		\While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
    			\State Pick $u$ at distance 3 from some vertex in $D$
    			\State $D \gets D \cup \{ w \}$
    		\EndWhile
    		\ForAll{$u \in D$}
    			\State Color $u$ with color $i$
    		\EndFor
    		\State $i \gets i + 1$
    		\ForAll{$u \in D$}
    			\State Remove $N(u)$ from $G$
    		\EndFor
    		\State Remove all isolated paths from G
    	\EndFor
    \EndWhile
    \State Color all removed isolated paths using color $i$
    \end{algorithmic}
  \end{algorithm}
  \end{frame}

>>>>

\usepackage{graphicx}
\usepackage[scale=2]{ccicons}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{algorithm, caption}
\usepackage[noend]{algpseudocode}
\usepackage[absolute,overlay]{textpos}
\usepackage{calc}
% \usepackage[texcoord,grid,gridunit=mm,gridcolor=red!10,subgridcolor=green!10]
% {eso-pic}

@@

\makeatletter
\newcommand{\algcolor}[2]{%
  \hskip-\ALG@thistlm\colorbox{#1}{\raisebox{0pt}[0.1cm][0cm]{\parbox{\dimexpr\linewidth-2\fboxsep}{\hskip\ALG@thistlm\relax #2}}}%
}
\newcommand{\algemph}[1]{\algcolor{Yellow}{#1}}
\makeatother

@@

    \begin{textblock*}{14cm}(1cm, 7.1cm) % {block width} (coords)
      To be conflict-free colored with 1 color, graph $G$ cannot contain $K_3$ or $K_4^{-3}$ as a minor. A graph is a \textbf{minor} if it can be formed by deleting and/or contracting edges from its parent graph. \only<3>{$G$ contains both $K_3$ and $K_4^{-3}$ as a minor and thus {\color{red}\textbf{cannot}} be conflict-free colored with 1 color.}
    \end{textblock*}

@@

    \only<1>{
      \begin{columns}
        \begin{column}{0.5\textwidth}
          \begin{algorithm}[H]
            \caption*{\textbf{Algorithm} IEDS}
            \scriptsize
            \begin{algorithmic}[1]
            \State $i \gets 1$
            \State Remove all isolated paths from $G$
            \While{$G$ is not empty}
              \State $D \gets \emptyset$
              \ForAll{components of $G$}
                \State Pick any vertex $v$
                \State $D \gets D \cup \{ v \}$
                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
                  \State Pick $u$ at distance 3 from some vertex in $D$
                  \State $D \gets D \cup \{ w \}$
                \EndWhile
                \ForAll{$u \in D$}
                  \State Color $u$ with color $i$
                \EndFor
                \State $i \gets i + 1$
                \ForAll{$u \in D$}
                  \State Remove $N(u)$ from $G$
                \EndFor
                \State Remove all isolated paths from G
              \EndFor
            \EndWhile
            \State Color all removed isolated paths using color $i$
            \end{algorithmic}
          \end{algorithm}
        \end{column}
        \begin{column}{0.5\textwidth}
          \begin{center}
            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/algorithm1.pdf}
                \caption*{A simple, undirected graph $G$}
              \end{figure}
            \end{textblock*}
          \end{center}
        \end{column}
      \end{columns}
    }

    \only<2-6>{
      \begin{textblock*}{8cm}(8cm, 6cm) % {block width} (coords)
        \begin{center}
          $i= 1$
        \end{center}
      \end{textblock*}
    }

    \only<2>{
      \begin{columns}
        \begin{column}{0.5\textwidth}
          \begin{algorithm}[H]
            \caption*{\textbf{Algorithm} IEDS}
            \scriptsize
            \begin{algorithmic}[1]
            \State \algemph{$i \gets 1$}
            \State \algemph{Remove all isolated paths from $G$}
            \While{$G$ is not empty}
              \State $D \gets \emptyset$
              \ForAll{components of $G$}
                \State Pick any vertex $v$
                \State $D \gets D \cup \{ v \}$
                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
                  \State Pick $u$ at distance 3 from some vertex in $D$
                  \State $D \gets D \cup \{ w \}$
                \EndWhile
                \ForAll{$u \in D$}
                  \State Color $u$ with color $i$
                \EndFor
                \State $i \gets i + 1$
                \ForAll{$u \in D$}
                  \State Remove $N(u)$ from $G$
                \EndFor
                \State Remove all isolated paths from G
              \EndFor
            \EndWhile
            \State Color all removed isolated paths using color $i$
            \end{algorithmic}
          \end{algorithm}
        \end{column}
        \begin{column}{0.5\textwidth}
          \begin{center}
            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/algorithm1.pdf}
                \caption*{A simple, undirected graph $G$}
              \end{figure}
            \end{textblock*}
          \end{center}
        \end{column}
      \end{columns}
    }

    \only<3>{
      \begin{textblock*}{8cm}(8cm, 6.5cm) % {block width} (coords)
        \begin{center}
          $D= \{\}$
        \end{center}
      \end{textblock*}

      \begin{columns}
        \begin{column}{0.5\textwidth}
          \begin{algorithm}[H]
            \caption*{\textbf{Algorithm} IEDS}
            \scriptsize
            \begin{algorithmic}[1]
            \State $i \gets 1$
            \State Remove all isolated paths from $G$
            \While{$G$ is not empty}
              \State \algemph{$D \gets \emptyset$}
              \ForAll{components of $G$}
                \State Pick any vertex $v$
                \State $D \gets D \cup \{ v \}$
                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
                  \State Pick $u$ at distance 3 from some vertex in $D$
                  \State $D \gets D \cup \{ w \}$
                \EndWhile
                \ForAll{$u \in D$}
                  \State Color $u$ with color $i$
                \EndFor
                \State $i \gets i + 1$
                \ForAll{$u \in D$}
                  \State Remove $N(u)$ from $G$
                \EndFor
                \State Remove all isolated paths from G
              \EndFor
            \EndWhile
            \State Color all removed isolated paths using color $i$
            \end{algorithmic}
          \end{algorithm}
        \end{column}
        \begin{column}{0.5\textwidth}
          \begin{center}
            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/algorithm1.pdf}
                \caption*{A simple, undirected graph $G$}
              \end{figure}
            \end{textblock*}
          \end{center}
        \end{column}
      \end{columns}
    }

    \only<4>{
      \begin{textblock*}{8cm}(8cm, 6.5cm) % {block width} (coords)
        \begin{center}
          $D= \{8\}$
        \end{center}
      \end{textblock*}

      \begin{columns}
        \begin{column}{0.5\textwidth}
          \begin{algorithm}[H]
            \caption*{\textbf{Algorithm} IEDS}
            \scriptsize
            \begin{algorithmic}[1]
            \State $i \gets 1$
            \State Remove all isolated paths from $G$
            \While{$G$ is not empty}
              \State $D \gets \emptyset$
              \ForAll{components of $G$}
                \State \algemph{Pick any vertex $v$}
                \State \algemph{$D \gets D \cup \{ v \}$}
                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
                  \State Pick $u$ at distance 3 from some vertex in $D$
                  \State $D \gets D \cup \{ w \}$
                \EndWhile
                \ForAll{$u \in D$}
                  \State Color $u$ with color $i$
                \EndFor
                \State $i \gets i + 1$
                \ForAll{$u \in D$}
                  \State Remove $N(u)$ from $G$
                \EndFor
                \State Remove all isolated paths from G
              \EndFor
            \EndWhile
            \State Color all removed isolated paths using color $i$
            \end{algorithmic}
          \end{algorithm}
        \end{column}
        \begin{column}{0.5\textwidth}
          \begin{center}
            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/algorithm1-slide-1.pdf}
                \caption*{A simple, undirected graph $G$}
              \end{figure}
            \end{textblock*}
          \end{center}
        \end{column}
      \end{columns}
    }

    \only<5>{
      \begin{textblock*}{8cm}(8cm, 6.5cm) % {block width} (coords)
        \begin{center}
          $D= \{8\}$
        \end{center}
      \end{textblock*}

      \begin{columns}
        \begin{column}{0.5\textwidth}
          \begin{algorithm}[H]
            \caption*{\textbf{Algorithm} IEDS}
            \scriptsize
            \begin{algorithmic}[1]
            \State $i \gets 1$
            \State Remove all isolated paths from $G$
            \While{$G$ is not empty}
              \State $D \gets \emptyset$
              \ForAll{components of $G$}
                \State Pick any vertex $v$}
                \State $D \gets D \cup \{ v \}$
                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
                  \State Pick $u$ at distance 3 from some vertex in $D$
                  \State $D \gets D \cup \{ w \}$
                \EndWhile
                \ForAll{$u \in D$}
                  \State Color $u$ with color $i$
                \EndFor
                \State $i \gets i + 1$
                \ForAll{$u \in D$}
                  \State Remove $N(u)$ from $G$
                \EndFor
                \State Remove all isolated paths from G
              \EndFor
            \EndWhile
            \State Color all removed isolated paths using color $i$
            \end{algorithmic}
          \end{algorithm}
        \end{column}
        \begin{column}{0.5\textwidth}
          \begin{center}
            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/algorithm1-slide-1.pdf}
                \caption*{A simple, undirected graph $G$}
              \end{figure}
            \end{textblock*}
          \end{center}
        \end{column}
      \end{columns}
    }
